Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-28 EMNLP-demo-paper/relatedWorks.tex
delete unrelated work

Visualizing and understanding neural models in nlp
Understanding Neural Networks through Representation Erasure
Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
End-to-End Non-Factoid Question Answering with an Interactive Visualization of Neural Attention Weights

%\subseciton{other}
DeepLife: an Entity-aware Search, Analytics and Exploration Platform for Health and Life Sciences
Visualizing and Curating Knowledge Graphs over Time and Space
GoWvis: a Web Application for Graph-of-Words-based Text Visualization and summarization
new/s/leak - Information Extraction and Visualization for an Investigative Data Journalists
Multi-modal Visualization and Search for Text and Prosody Annotations
Visual Error Analysis for Entity Linking
JoBimViz: A Web-based Visualization for Graph-based Distributional Semantic Models
WA-Continuum: Visualising Word Alignments across Multiple Parallel Sentences Simultaneously
Scattertext: a Browser-Based Tool for Visualizing how Corpora Differ
Interactive Visual Analysis of Transcribed Multi-Party Discourse
Visualization, Search, and Error Analysis for Coreference Annotations

>>>>

Visualizing and understanding neural models in nlp
Understanding Neural Networks through Representation Erasure

Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
\textcolor{blue}{Lee visualizes the beam search and attention component in the NMT model. The work allows user involve into the decision-making process by enabling dynamic change the probability for the next step of the search tree or change the weight value of the attention.}

End-to-End Non-Factoid Question Answering with an Interactive Visualization of Neural Attention Weights
\textcolor{blue}{Instead of visualizing the attention matrix directly, the system shows the text context and highlights the critical phrase, which used to answers the questions, using color map. In this platform, user able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.}
